Discovery of s-process enhanced stars in the LAMOST survey

### 2018-09-13 article/ms.tex
paper progress

Here we present the discovery of 895 stars enriched in s-process elements from the LAMOST spectra using a data-driven approach. This sample constitutes the largest number of s-process enhanced stars ever discovered. Our sample includes; 187 s-process candidates that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 659 stars that show only strontium enhancement. Our entire s-process candidate sample exists within temperature and luminosity ranges not enveloped by the AGB?, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion. The majority of our barium stars ($95\%$) show strong carbon enhancements yet, only 5 candidates ($<3$\,\%) show evidence of sodium enhancement, in tension with previous observations of enhanced Na among s-process candidates. We argue this may have been a selection bias? in previous studies. Our kinematical analysis reveals our sample is composed of 97\% disk stars, and 3\% with velocity consistent to the halo. A comparison with AGB yields suggests the main neutron source responsible for Ba and Sr enhancements is the $\text{C}^{13}$(\textrm{$\alpha$},n)$\text{O}^{16}$ reaction chain. Theoretical models show that this source is dominant in low-mass AGB stars. We conclude that the progenitors for s-process enhancement in our sample are AGB companion stars with masses $1 - 3\,M_{\odot}$.

@@

The abundance of elements created through the slow neutron-capture process (s-process), is a measure of the nucleosynthetic reactions that occur primarily in Asymptotic Giant Branch (AGB) stars. Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are commonly referred to as 'barium stars' \citep{Bidelman1951}. The naming convention associated with 'barium stars' is historical, for the purposes of this paper it is necessary to classify definitions used for subsequent discussions. Stars with Ba and Sr enrichment will be refereed to as s-process candidates, and singular enhancement samples will be named according to their respective element. Metallicity-dependent classifications also exist in the literature. Metal-poor stars ([Fe/H] $\approx$ [0,-1.2]) enriched by s-process elements are classically refereed to as CH stars, we will simply define them as metal poor s-process candidates. An abundance criteria may also be used to define s-process enrichment, this is typically taken as threshold of $\rm[Ba/Fe]\geq +0.3$ \citep{malaney1988}. For the purposes of this paper, s-process enrichment will be determined solely on the presence significant flux residuals as described in Section \ref{sec:cand}.
S-process candidates can be classified as either extrinsic or intrinsic objects. Extrinsic s-process stars are stellar phenomena exhibiting an enhancement as the result of some polluting process. Stars intrinsically enhanced in s-process elements are known as AGB S stars. These stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase. During this stage of nucleosynthesis, the s-process produces an over-abundance of both carbon and heavy elements. The thermal pulsing cycle transports these elements to surface of TP-AGB stars. According to the mass-transfer hypothesis, extrinsic s-process stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}. Both dynamical systems require a binary configuration with a previous TP-AGB companion star (AGB S star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determined 85\% of all s-process candidates are in binary systems. They further claimed that stars which appeared to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small ranges \citep{pourbaix2004}. For these reasons, the properties and occurrence rate of s-process candidates are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.

@@

Occurring in the interior of AGB stars, the s-process synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}. During the subsequent TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core. These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions. While simultaneously, forcing the star to expand and pushing the H-shell out to cooler regions \citep{karakas2002}. The convective envelope will then move inwards towards regions previously mixed by the thermal pulse driven convective zones. This phase of expansion and resulting inward movement is defined as the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, the TDU is responsible for the surface enrichment in $^{12}$C and heavy elements produced by the s-process \citep[e.g.,][]{busso2001}. Post dredge up the star contracts, reigniting the H-shell, and producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and the frequency depends on the initial mass, composition, and mass-loss rate of the star.

S-process candidate can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$ \citep{karakas2016cp}. The minimum mass is defined by the onset of core helium burning, and the maximum by core carbon burning. The age of these stars varies considerably, with some reaching ages $\approx$ 12\,Gyr in metal-poor globular clusters. Less massive metal-rich stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}. The majority s-process candidates are observed to be members of the disk \citep{jorissen1993,gomez1997,mennessier1997}. In \citet{pereira2011}, it is shown that metal-rich s-process candidates share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population. \cite{jorissen1993} relates galactic position to the extrinsic or intrinsic nature of the s-process candidate. They show that intrinsically enhanced stars are more concentrated towards the galactic plane than extrinsic enhanced stars.

@@

\section{Methods} \label{sec:methods}
\subsection{LAMOST analysis}
\subsubsection{Data-driven analysis}
The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for 2,207,189 stars in their second data release \citep{luo2015}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived by \citep{ho2017} using a \emph{The Cannon} \citet{ness2016}, with labels for 9,952 giant stars in common between LAMOST and the APOGEE survey. We note that this sample is limited to giant stars, implying that we would not identify dwarf s-process enhanced stars. Cross-validation tests shows that the typical uncertainties are approximately 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M]. These uncertainties are comparable to the those present in APOGEE \citep{alam2015}.

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$, indicating a stronger absorption line than expected by the model.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2) of the rest frame laboratory model.
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item The LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
We use visual inspection with all candidates to exclude any results containing false positives: candidates with data reduction issues; apparent absorption finer then the spectral resolution; or overly noisy normalised LAMOST spectra. This approach discovers 895 s-process rich candidates which are provided in Table 1. This sample consists of; 187 s-process candidates, 49 barium enriched stars, and 659 stars with strontium enrichment. It is the largest collection of s-process enhanced stars ever discovered, with the next sample of significant size containing 182 s-process candidates \citep[e.g.,][]{decastro2016}.

@@

\subsubsection{Enhancements due to sodium, technetium, and carbon} \label{sec:other enhancements}
Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars. We? performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 187 s-process candidates. For sodium enrichment, we required significant absorption in the doublet lines at 5889\,\AA\ and 5895\,\AA\. Only 5/187 s-process candidates met this criteria. For technetium enhancement, we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium enhancement before it would be visible in a high S/N LAMOST spectrum. We found that 51 s-process candidates exhibited some level of significant enhancement at the single absorption line 4238\,\AA. Single line enrichment discovered by our data driven approach are very likely attributed to data reduction/calibration artefacts present. These artefacts exist within in our data as a result of fitting a model to the LAMOST spectral data. As such, the 51 stars enhanced in a single Tc line can be ruled out as false positives. For carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA, of which 178/187 s-process candidates exhibited significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

@@

\subsection{Abundance analysis}
We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citet{ho2017}. Following the procedure outlined in \citet{casey2014}, we measured the strength of \ion{Ba}{II} (4554\,\AA, 4934\,\AA, and 6496\,\AA) and \ion{Sr}{II} (4077\,\AA\ and 4215\,\AA) absorption lines by spectral synthesis, using s-process isotopic ratios from \citet{sneden08}. The abundance ratios we estimate from high-resolution spectra are in excellent agreement with our estimates from LAMOST spectra, all agreeing within the joint $1.2\sigma$. Specifically, for J09162834+0259348 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$. The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ from our Magellan/MIKE spectra, and $0.90 \pm 0.22$ from LAMOST. Finally, for J09162834+0259348 we find $[{\rm Ba/Fe}] = 0.94 \pm 0.12$ from high-resolution spectra and $[{\rm Ba/Fe}] = 0.80 \pm 0.26$ from low-resolution spectra. Uncertainties on abundances derived from high-resolution spectra are taken as the standard deviation of multiple line measurements. The high-resolution abundances we find help validate our methodology for candidate selection, and for estimating abundances from LAMOST spectra.

@@

\subsection{Extrinsic or intrinsic}
S-process enrichment can be explained by intrinsic or extrinsic phenomena. Intrinsically enhanced s-process candidates must be massive enough to reach the TP-AGB phase, and extrinsic s-process candidates must be in a binary with a previously polluting TP-AGB star companion (AGB S star). Previous literature \citep{van2017} states only 33\% of their sample are post-main-sequence s-process candidates (extrinsic). In comparison, Figure \ref{fig:figure2} shows that the majority of our sample have temperatures and luminosity not covered by the AGB. This highlights that our sample does not contain stars evolved enough to reach the TP-AGB phase and therefore, must be extrinsic s-process candidates. This is in agreement with our sample selection given we were predominantly restricted to RGB stars. However stars with temperatures below 3800K in Figure \ref{fig:figure2} are consistent with being AGB stars, and their intrinsic or extrinsic nature is not certain.

@@

\subsection{Sodium enhancement}
Sodium overabundances observed in the atmospheres of giants are primarily synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}. Sodium is transported to the surface via mixing during the first dredge-up and stars with masses more than $1.5\,M_\odot$ can show enhanced sodium abundances \citep{denissenkov1987,smiljanic2012}. \citet{antipova2004} reported  enhanced sodium in 3 of their 16 barium star candidates. They relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase and suggest that [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values. Similarly, \citet{decastro2016} proposes a possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend is present in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.

@@

Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhancement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic s-process candidates. Our analysis searches for flux residuals around the Tc enhancement lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. We found 51/187 of our s-process candidates to show enhanced Tc at the single line 4238,\AA. The majority (46/51) have $\log{g} > 2$ suggesting they cannot be AGB S stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event. However we caution that Tc enhancement is usually a very weak signature and would require multiple lines of enhancement. Since all 51 matches were at single lines we concluded Tc enhanced candidates are more likely a result of data artefacts. Also, it is universally known that numerous Tc lines are considerably blended by other s-process enhancement lines \citep[e.g.,][]{van1999}. We therefore conclude our analysis finds no enhanced Tc s-process candidates and is in agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}. The absence of Tc indicates our s-process candidates are not massive enough to produce the element, and suggests that our sample is populated solely by extrinsic s-process candidates.

@@

\subsection{Carbon bands}
During the AGB phase of a star, carbon abundance is a product of helium fusion via the triple-alpha process. Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star. Our analysis identifies carbon enhanced candidates by searching for flux residuals in the CH and G band regions at lines 4050\,\AA\hspace{0.5mm} and 4550\,\AA. We found 178/187 of our s-process candidates to have carbon enrichment (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$). These 178 stars have in a metallicities ranging of 0 to -1.2, and are classically referred to as CH stars \citep[e.g.][]{luck1991, mcclure1997}, we simply define them as metal poor s-process candidates.

\subsection{Comparison to AGB yields}
In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 187 s-process candidates identified in LAMOST. Although the [Ba/Sr] ratio is quite noisy ($\sim$0.2\,dex) the overall metallicity [Fe/H] is quite precise (0.1\,dex). The final surface s-process index [Ba/Sr] seen in Figure \ref{fig:figure3} represents degree of the s-process pollution and is an indication of the binary AGB companion's mass. The [Ba/Sr] yields for our s-process candidates follow similar trends to previous studies \citep{fishlock2014,cristallo2015,karakas_lugaro2016}. This suggests that the main neutron source for s-process enhancement in our sample is the $\text{C}^{13}$(\textrm{$\alpha$},n)$\text{O}^{16}$ reaction chain. Theoretical models show that this source is dominant in low-mass AGB stars and it follows, that most of the progenitors for s-process enhancement in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$. However our results do not indicate when the mass transfer occurred, and our candidates fitting these theoretical yields may not have the correlating binary companion masses. Mass transfer may have occurred early on in the AGB S binary companion star's lifespan. The resulting [Ba/Sr] abundance present in our s-process candidates and those not approximated by theoretical curves may reflect pollution from a lower AGB S star mass. Our s-process candidates that deviate from this relationship may also represent the possibly more massive and exceptionally rarer AGB S stars within our sample.

@@

The majority of our sample show pro-grade orbits that were consistent with membership in the Milky Way disk. Figures \ref{fig:figure4} and \ref{fig:figure5} illustrate the galactic position of each class of s-process enhanced star investigated. For our entire 898 sample, Figure \ref{fig:figure4} shows 97\% reside within the galactic disk  and 3\% with velocity consistent to the halo. Our results show similar trends to the literature, samples from \cite{gomez1997} and  
\cite{decastro2016} present populations with $\sim$90\% thin disk membership. \cite{pereira2011}’s limited sample (12 stars) entirely resides within the disk. \cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, concluding intrinsic s-process candidates are more concentrated towards the galactic plane. Since our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources. However as shown in Figure \ref{fig:figure4} our extrinsically s-process enhanced sample concentrates towards the galactic plane. We can propose that the sample in \cite{jorissen1993} was not sufficiently large enough to represent the overarching galactic distribution of extrinsic S stars. On the contrary, our findings may be reflective of our sample's bias towards finding extrinsic s-process candidates since we were limited mainly to RGB stars. It may not be representative of the overall galactic position of enhanced s-process stars.

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth]{histogram.pdf}
	\caption{Galactic latitude ([$|b^{\circ}|$]; x-axis) shown for: number of s-process enhanced candidates matched with Gaia DR2, and s-process candidates as a fraction of the LAMOST sample matched with Gaia DR2}
	\label{fig:figure5}
\end{figure}

>>>>

Here we present the discovery of 895 s-process candidates from 454,180 giant stars observed by LAMOST using a data-driven approach. This sample constitutes the largest number of s-process enhanced stars ever discovered. Our sample includes; 187 s-process candidates that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 659 stars that show only strontium enhancement. Most of our sample are within temperature and log g ranges consistent with RGB populations, this is consistent with our selection bias towards finding RGB stars. The majority of our s-process candidates ($95\%$) show strong carbon enhancements yet, only 5 candidates ($<3$\,\%) show evidence of sodium enhancement, in tension with previous observations of enhanced Na among s-process candidates. We argue this may have been a systematic bias in previous studies. Our kinematical analysis reveals our sample is composed of 97\% disk stars, and 3\% with velocity consistent to the halo. A comparison with AGB yields suggests the main neutron source responsible for Ba and Sr enhancements is the $\text{C}^{13}$(\textrm{$\alpha$},n)$\text{O}^{16}$ reaction chain. Theoretical models show that this source is dominant in low-mass AGB stars. We conclude that the progenitors for s-process enhancement in our sample are AGB companion stars with masses $1 - 3\,M_{\odot}$.

@@

The abundance of elements created through the slow neutron-capture process (s-process) is a measure of the nucleosynthetic reactions that occur primarily in Asymptotic Giant Branch (AGB) stars. Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are commonly referred to as 'barium stars' \citep{Bidelman1951}. The naming convention associated with 'barium stars' is historical, for the purposes of this paper it is necessary to classify definitions used for subsequent discussions. Stars with Ba and Sr enrichment will be refereed to as s-process candidates, and singular enhancement samples will be named according to their respective element. Metallicity-dependent classifications also exist in the literature. Metal-poor stars ([Fe/H] $\approx$ [0,-1.2]) enriched by s-process elements are classically refereed to as CH stars, we will simply define them as metal poor s-process candidates. An abundance criteria may also be used to define s-process enrichment, this is typically taken as threshold of $\rm[Ba/Fe]\geq +0.3$ \citep{malaney1988}. For the purposes of this paper, s-process enrichment will be determined solely on the presence significant flux residuals as described in Section \ref{sec:cand}.
S-process candidates can be classified as either extrinsic or intrinsic objects. Extrinsic s-process stars are stellar phenomena exhibiting an enhancement as the result of some polluting process. Stars intrinsically enhanced in s-process elements are known as AGB S stars. These stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase. During this stage of nucleosynthesis, the s-process produces an over-abundance of both carbon and heavy elements. The thermal pulsing cycle transports these elements to surface of TP-AGB stars. According to the mass-transfer hypothesis, extrinsic s-process stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}. Both dynamical systems require a binary configuration with a previous TP-AGB companion star (AGB S star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determined 85\% of all s-process candidates are in binary systems. They further claimed that stars which appeared to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small ranges \citep{pourbaix2004}. For these reasons, the properties and occurrence rate of s-process candidates are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.

@@

Occurring in the interior of AGB stars, the s-process synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}. During the subsequent TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core. These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions. While simultaneously forcing the star to expand and pushing the H-shell out to cooler regions \citep{karakas2002}. The convective envelope will then move inwards towards regions previously mixed by the thermal pulse driven convective zones. This phase of expansion and resulting inward movement is defined as the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, the TDU is responsible for the surface enrichment in $^{12}$C and heavy elements produced by the s-process \citep[e.g.,][]{busso2001}. Post dredge up the star contracts, reigniting the H-shell and producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and the frequency depends on the initial mass, composition, and mass-loss rate of the star.

S-process candidates can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$ \citep{karakas2016cp}. The minimum mass is defined by the onset of core helium burning, and the maximum by core carbon burning. The age of these stars varies considerably, with some reaching ages $\approx$ 12\,Gyr in metal-poor globular clusters. Less massive metal-rich stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}. The majority of s-process candidates are observed to be members of the disk \citep{jorissen1993,gomez1997,mennessier1997}. In \citet{pereira2011}, it is shown that metal-rich s-process candidates share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population. \cite{jorissen1993} relates galactic position to the extrinsic or intrinsic nature of the s-process candidate. They determine the scale height for their intrinsic candidates and state they are concentrated towards the galactic plane whilst their extrinsic s-process candidates are uniformly distributed.

@@

\section{Methods} \label{sec:methods}
\subsection{LAMOST analysis}
\subsubsection{Data-driven analysis}
The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for 2,207,189 stars in their second data release \citep{luo2015}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived by \citep{ho2017} using a \emph{The Cannon} \citet{ness2016}, with labels for 9,952 giant stars in common between LAMOST and the APOGEE survey. Our sample is limited entirely to giants implying that we would not identify dwarf s-process enhanced stars. Cross-validation tests shows that the typical uncertainties are approximately 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M]. These uncertainties are comparable to the those present in APOGEE \citep{alam2015}.

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$, indicating a stronger absorption line than expected by the model.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2) of the rest frame laboratory model.
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item The LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
We use visual inspection with all candidates to exclude any results containing false positives: candidates with data reduction issues; apparent absorption finer then the spectral resolution; or overly noisy normalised LAMOST spectra. This approach discovers 895 s-process rich candidates which are provided in Table 1. This sample consists of; 187 s-process candidates, 49 barium enriched stars, and 659 stars with strontium enrichment. It is the largest collection of s-process enhanced stars ever discovered.

@@

\subsubsection{Enhancements due to sodium, technetium, and carbon} \label{sec:other enhancements}
Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars. We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify negative flux residuals for enhancement in sodium, technetium, or carbon. For sodium enrichment, we required significant absorption in the doublet lines at 5889\,\AA\ and 5895\,\AA\. Only 5/187 s-process candidates met this criteria. For technetium enhancement, we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium enhancement before it would be visible in a high S/N LAMOST spectrum. We found that 51 s-process candidates exhibited some level of significant enhancement at the single absorption line 4238\,\AA. Single line enrichment discovered by our data driven approach are very likely attributed to data reduction/calibration artefacts present. These artefacts exist within in our data as a result of fitting a model to the LAMOST spectral data. As such, the 51 stars enhanced in a single Tc line can be ruled out as false positives. For carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA, of which 178/187 s-process candidates exhibited significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

@@

\subsection{Abundance analysis}
We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citet{ho2017}. Following the procedure outlined in \citet{casey2014}, we measured the strength of \ion{Ba}{II} (4554\,\AA, 4934\,\AA, and 6496\,\AA) and \ion{Sr}{II} (4077\,\AA\ and 4215\,\AA) absorption lines by spectral synthesis, using s-process isotopic ratios from \citet{sneden08}. The abundance ratios we estimate from high-resolution spectra are in excellent agreement with our estimates from LAMOST spectra, all agreeing within the joint $1.2\sigma$. For J09162834+0259348 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$. The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ from our Magellan/MIKE spectra, and $0.90 \pm 0.22$ from LAMOST. For J08351472-0548480 we find $[{\rm Ba/Fe}] = 0.94 \pm 0.12$ from high-resolution spectra and $[{\rm Ba/Fe}] = 0.80 \pm 0.26$ from low-resolution spectra. Uncertainties on abundances derived from high-resolution spectra are taken as the standard deviation of multiple line measurements. The high-resolution abundances we find help validate our methodology for candidate selection, and for estimating abundances from LAMOST spectra.

@@

\subsection{Extrinsic or intrinsic}
S-process enrichment can be explained by intrinsic or extrinsic phenomena. Intrinsically enhanced s-process candidates must be massive enough to reach the TP-AGB phase, and extrinsic s-process candidates must be in a binary with a previously polluting TP-AGB star companion (AGB S star). Previous literature \citep{van2017} \hspace{0.3mm} states only 33\% of their sample are post-main-sequence s-process candidates (extrinsic). In comparison, Figure \ref{fig:figure2} shows that the majority of our sample are within temperature and log g ranges consistent with RGB populations. This highlights that our sample does not contain stars evolved enough to reach the TP-AGB phase and therefore, must be extrinsic s-process candidates. This is in agreement with our sample selection bias given we were predominantly restricted to RGB stars. However stars with temperatures below 3800K in Figure \ref{fig:figure2} are possible AGB candidates, and their intrinsic or extrinsic nature is not certain.

@@

\subsection{Sodium enhancement}
Sodium overabundances observed in the atmospheres of giants are primarily synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}. Sodium is transported to the surface via mixing during the first dredge-up and stars with masses more than $1.5\,M_\odot$ can show enhanced sodium abundances \citep{denissenkov1987,smiljanic2012}. \citet{antipova2004} reported  enhanced sodium in 3 of their 16 s-process candidates. They relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase, and suggest that [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values. Similarly, \citet{decastro2016} proposes a possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend is present in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.

@@

Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhancement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic s-process candidates. Our analysis searches for flux residuals around the Tc enhancement lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. We found 51/187 of our s-process candidates to show enhanced Tc at exclusively 4238,\AA. The majority (46/51) have $\log{g} > 2$ suggesting they cannot be AGB S stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event. However we caution that Tc enhancement is usually a very weak signature, would require multiple lines of enhancement, and is considerably blended by other s-process enhancement lines \citep[e.g.,][]{van1999}. Since all 51 matches were at a single line we surmise Tc enhanced candidates are more likely a result of data artefacts. We therefore conclude our analysis finds no Tc enhanced candidates and is in agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}. The absence of Tc indicates our sample is populated solely by extrinsic s-process candidates and a recent mass transfer event is not the source of our s-process enhancement.

@@

\subsection{Carbon bands}
During the AGB phase of a star, carbon abundance is a product of helium fusion via the triple-alpha process. Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star. Our analysis identifies carbon enhanced candidates by searching for flux residuals in the CH and G band regions near 4300\,\AA. We found 178/187 of our s-process candidates to have carbon enrichment (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$). These 178 stars have metallicities ranging of 0 to -1.2 and are classically referred to as CH stars \citep[e.g.][]{luck1991, mcclure1997}. We simply define them as metal poor s-process candidates.

\subsection{Comparison to AGB yields}
In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 187 s-process candidates identified in LAMOST. Although the [Ba/Sr] ratio is quite noisy ($\sim$0.2\,dex) the overall metallicity [Fe/H] is quite precise (0.1\,dex). The final surface s-process index [Ba/Sr] seen in Figure \ref{fig:figure3} represents degree of the s-process element pollution, and is an indication of the binary AGB companion's mass. The [Ba/Sr] yields for our s-process candidates follow similar trends to previous studies \citep{fishlock2014,cristallo2015,karakas_lugaro2016}. This suggests that the main neutron source for s-process enhancement in our sample is the $\text{C}^{13}$(\textrm{$\alpha$},n)$\text{O}^{16}$ reaction chain. Theoretical models show that this source is dominant in low-mass AGB stars and it follows, that most of the progenitors for s-process enhancement in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$. However our results do not indicate when the mass transfer occurred, and our candidates fitting these theoretical yields may not have the correlating binary companion masses. Mass transfer may have occurred early on in the AGB S binary companion star's lifespan. The resulting [Ba/Sr] abundance present in our s-process candidates and those not approximated by theoretical curves may reflect pollution from a lower AGB S star mass. Our s-process candidates that deviate from this relationship may also represent the possibly more massive and exceptionally rarer AGB S stars within our sample.

@@

The majority of our sample show pro-grade orbits that were consistent with membership in the Milky Way disk. Figures \ref{fig:figure4} and \ref{fig:figure5} illustrate the galactic position for each class of s-process enhanced star investigated. For our entire 898 sample, Figure \ref{fig:figure4} shows 97\% reside within the galactic disk and 3\% with velocity consistent to the halo. Our results show similar trends to the literature, samples from \cite{gomez1997} and  
\cite{decastro2016} present populations with $\sim$90\% thin disk membership. \cite{pereira2011}'s limited sample (12 stars) entirely resides within the disk. \cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature (see their Sect. 4.2). They determine the scale height for their intrinsic candidates and state they are concentrated towards the galactic plane whilst their extrinsic s-process candidates are uniformly distributed. Figure \ref{fig:figure5} illustrates all absolute galactic latitudes for our sample, after correcting for the LAMOST selection factor we see a uniform galactic distribution for all our extrinsic s-process candidates in-agreement with \citet{jorissen1993}. Since our sample is uniformly distributed we cannot comment on the scale height of our s-process candidates.

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth]{histogram.pdf}
	\caption{Absolute galactic latitude ([$|b^{\circ}|$]; x-axis) and the number of corresponding stars ([$N$] and [$N\mathbin{/}N_{LAMOST}$]; y-axis) shown for: s-process enhanced candidates matched with Gaia DR2, and the s-process candidates as a fraction of the LAMOST sample matched with Gaia DR2 }
	\label{fig:figure5}
\end{figure}
